Group 5 Report

### 2022-08-02 Report/Group 5 report.Rmd
Adding libraries.

```{r Setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, error = FALSE, message = FALSE, out.width = "100%")
line <- "***"
```

>>>>

```{r Setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, error = FALSE, message = FALSE, out.width = "100%")
```

```{r libraries, include=FALSE}
library(tidyverse)
library(janitor)
library(rvest)
library(MetBrewer)
```

```{r line, include=FALSE}
line <- "***"
```

```{r}

```
